---
title: "Lab 8 test"
author: "Natalie Rossington"
date: "3/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(leaflet)
library(sf)
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
library(corrplot)
```

```{r}
oilspills <- read.csv("oil_spills.csv")
```
```{r}
df_loc <- oilspills %>% 
  filter(Accident.State == "TX" & Accident.Year == 2016) %>% 
  select(Latitude, Longitude, Net.Loss..Barrels.)

colnames(df_loc) <- c("latitude", "longitude", "net_loss")

oil_sf <- st_as_sf(df_loc, coords = c("longitude","latitude"), crs = 4326)

leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()
```


##Make a Tmap plot with the Texas state shapefile - if you need bounds, you need a shapefile
```{r}
states <- st_read(dsn = ".", layer = "states")

tex_border <- states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)

plot(tex_border)

tm_shape(tex_border) +
  tm_polygons() +
  tm_shape(oil_sf) +
  tm_dots(size = 0.3)

#Are these spatially random (CSR)? or non random?
```

##Convert the data to spatial points patterns - combination of point data dnt he bounding window
```{r}
spill_sp <- as(oil_sf, "Spatial")
spill_ppp <- as(spill_sp, "ppp") ###specific version of spatial data to do point pattern analysis
tx_sp <- as(tex_border, "Spatial")
tx_owin <- as(tx_sp, "owin")

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)
```

##Density Plot
```{r}
plot(density(all_ppp, sigma = 0.4))
```

##Quadrat test for spatial evenness
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5) #nx = 5, five regions horizontally
```{r}
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5) #nx = 5, five regions horizontally
oil_qt

#performs chi squared test, which means we can reject the null hypothesis of CSR or spatial evenness, retain alternative that the data are NOT CSR (or..not evenly distributed), calculates relative to area of the quadrat

plot(all_ppp)
plot(oil_qt, add = TRUE, cex = 0.5)
```

##G-function for nearest neighbor analysis
```{r}
r <- seq(0,1, by = 0.01)
oil_gfun <- envelope(all_ppp, fun = Gest, r = r, nsim = 100)

plot(oil_gfun)

ggplot(oil_gfun, aes(x = r, y = obs)) + 
  geom_line() + 
  geom_line(aes(x = r, y = theo), color = "red") #theo, theoretical r
```

##Nearest neighbor using the L-function (Ripley's K but standardized)
```{r}
r2 <- seq(0,3, by = 0.5)

oil_lfun <- envelope(all_ppp, fun = Lest, r = r2, nsim = 20, global = TRUE)

ggplot(oil_lfun, aes(x = r2, y = obs)) +
  geom_line(color = "black") +
  geom_line(aes(x = r2, y = theo), color = "red")
```

